---
title: "Read data from LIMS datawarehouse database using R"
description: "Accessing report data from the INBO laboratory, which is stored in a DWH in LIMS. Only accessable for INBO employees connected to the INBO network"
authors: [pietervsd]
date: 2023-10-17
categories: ["r"]
tags: ["lims", "r", "data"]
output: 
  html_document:
    toc: true
  md_document:
    preserve_yaml: true
    variant: gfm+footnotes
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

# Introduction

## Situation

The INBO laboratory uses a LIMS system to manage the result data. All results are saved in a SQL server database.

Daily, the results are loaded into a data warehouse (DWH) that makes querieing easier. All tables are directly connected to the base result table.

The INBO scientists can retreive their lab data using R with or without the help of this `inbolims` package, but this package shoud ease it.

## Usage

To use this package, it should be installed via github. To enable this, it is best to install the package `remotes`. Furthermore the package tidyverse should be installed.

```{r prep, cache=TRUE, results='hide'}
install.packages(c("remotes", "tidyverse"))
remotes::install_github("inbo/inbolims")
```

Load the tidyverse library and the inbolims library.

```{r lib}
library(tidyverse)
library(inbolims)
```

# Import Lims Data

## Make the database connection

Before data can be retrieved from the lims datawarehouse, a connection to the database is needed. The package contains a function for this `lims_connect`.
`lims_connect` without additional arguments will connect to the database in the production environment using the `DBI` package as a trusted connection via the windows active directory.

If a connection to the test (uat) environment, use the parameter `deployment = "uat"`. If connection should happen via `RODBC` use the argument `use_RODBC = TRUE`

When you have access to the database, but are not in the user list of INBO, you can use your database user-name and password via de parameter `uidpwd ="uid=user001;pwd=secret;"`, replacing the user name and password.

```{r connect}
#maak connectie met databank
connection <- lims_connect()
```

## Retrieve results for a project

Once the connection object is created, this object is used to retrieve the data.
By default all data are retrieved using a  default sql template. One or more projects can be specified via the argument `project = "projectName"`. Multiple projects can be specified using the `c` function: `project = c("ProjectName1", "ProjectName2")`.
The results are a R `tibble` dataset that can easily viewed using `view`

```{r basics1, cache = TRUE}
#haal de rapportgegevens binnen uit de databank
report_data <- read_lims_data(connection = connection, 
                              project = c("I-23W001-02"))
```

```{r basics2, cache = TRUE}
#Bekijk de gegevens in R
report_data %>% view()
```

It is possible to customize the results you get, although some minimal fields should always be present. Some  templates are made available and can be found with
`list_availaible_templates()` <<<FUNCTIE NOG MAKEN>>>. 
You can make your own template based on one of these <<<FUNCTIE NOG MAKEN>>>

If you want to get more advanced you can even specify your own query based on the query used in this package.


```{r basics3, cache = TRUE}
#haal de rapportgegevens binnen uit de databank
report_data <- read_lims_data(connection = connection, 
                               project = c("I-23W001-02"), 
                               sql_template = "default", 
                               show_query = FALSE)
```



## Custom query

# Using the data

## Sample overview


```{r stalen}
staaloverzicht <- lims_report_samples(report_data)
view(staaloverzicht)

## Crosstable

```{r kruistabel}
kruistabel <- lims_report_xtab(report_data)
view(kruistabel)

# Exporting the results

```{r export}
lims_report_export(kruistabel, path = "test_xtab.csv")
lims_report_export(report_data, path = "test.csv")
```



```


```





